Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2020-05-27 Manuscript/manuscript.Rmd
added to discussion

>>>>

The performance of *preciseTAD* was found to be empirically better than both ARROWHEAD and PEAKACHU ground truth boundaries. *preciseTAD* provides bp resolution predicted boundaries, thereby alleviating resolution limitations of conventional TAD-callers. We show that, unlike ARROWHEAD, *preciseTAD* does not inflate the number of predicted boundaries, instead, providing only the most biologically meaningful boundaries. *preciseTAD* boundaries we found to be more enriched for known architectural transcription factors including CTCF, RAD21, SMC3, and ZNF143. Likewise *preciseTAD* boundaries were found to be more conserved between GM12878 and K562 cell lines, further highlighting their biological significance.
